\chapter{Introduction}
Giving a general overview of the report.\\
\\



\section{Organization Of the Report}

\begin{itemize}
\item Chapter 2 explains the simulation environment we built.
\item Chapter 3 contains a description of the algorithms we decided to use.
\item Chapter 4 contains the results of our simulations.
\item Chapter 5 contains a discussion of our results, comparison and conclusions.
\end{itemize}




\section{Background}
The objective of this section is to give a short theoretical
background of optimization.
\subsection{What is optimization}
What is optimization?\\
What is an optimal solution?\\
Non-optimal solutions?\\
Good solutions and computational time?\\
\\

\subsection{(the need for) a near optimal solution}
Giving a very short background for the following section. 

\subsection{P \& NP problems}
explain what P and NP-hard problems is, and what consequenses it yields. 

\subsection{Heuristic methods}
Explanation of what heuristic methods is, and how one sacrifices
optimality for gain in computational time.\\

\section{Problem formulation}
The essentials of our problem formulation today is "To test
implementation of greedy approach, tabu search and genetic programming
and evaluation." The exact formulation is in progress...


\subsection{Approach}
A description of our approach to the problem. Describing the overview
of our approach. Mentioning the creation of an testing enviroment,
choice and application of heuristics and target data to evaluate the effectiveness.

