\chapter{Introduction}
Giving a general overview of the report.\\
\\



\section{Organization Of the Report}

\begin{itemize}
\item Chapter 2 explains the simulation environment we built.
\item Chapter 3 contains a description of the algorithms we decided to use.
\item Chapter 4 contains the results of our simulations.
\item Chapter 5 contains a discussion of our results, comparison and conclusions.
\end{itemize}




\section{Background}
The objective of this section is to give a short theoretical
background of optimization.
\subsection{What is optimization}
What is optimization?\\
What is an optimal solution?\\
Non-optimal solutions?\\
Good solutions and computational time?\\
\\
Optimization is a mathematical discipline, for solving various types of problems. In the simplest case this means seeking a solution, within an allowed set, that minimizes or maximizes a real valid function.
More generally, it means finding "best available" values of some objective function given a defined domain.\\


%%\begin{align*}
%%a_{11}  x_1 & + & \cdots  &  & +a_{1n} x_n & & = && b_1 \\
 %%\vdots       &&   \ddots     && \vdots & & && \vdots  \\
%%a_{m1} x_1 & +& \cdots  & &+ a_{nm} x_n & &= && b_m \\
%%\end{align*}


%%%%felix producerat
%%%% sker annat ord fr: "feeld of optimization" "one has"

In the new age of computers the field of optimization is heavily linked to the field of computer science. Needles to say the vast majority of problems is today, in one way or another, solved by a computer. One usually speaks of different kinds of algorithms, that in (some sense/the linear case) process a overdetermined equation system.\\\\
When solving practical problems with these algorithms  these overdetermined equation systems... \\\\
""""in real life"""" many problem depends on a vast amount of different variables, but thanks to computers this is not a problem, or is it?\\
The fact is: that it is a problem, for complicated problems these overdetermined equation system becomes very/to time consuming to process. \\
\hspace{1in} Due to this fact the field of optimization is much about developing algorithms that tackle this problem (the computational time).

\subsection{(the need for) a near optimal solution}
One drastic "solution" to minimize the computational time is to sacrifice optimality. The question is of course: to what end?\\
When evaluating this question one needs to look at what type of problem one has (to see what one has to gain).\\
One problem type relevant to this report is NP-problems.

\subsection{P \& NP problems}
NP-hard problems may be of any type: decision problems, search problems, or optimization problems.\\\\
Useful sources about P and NP.\\
http://en.wikipedia.org/wiki/NP\_(complexity)\\
http://en.wikipedia.org/wiki/NP\\
http://en.wikipedia.org/wiki/NP-complete\\
http://en.wikipedia.org/wiki/NP-hard\\
http://en.wikipedia.org/wiki/P\_versus\_NP\_problem\\

\subsection{Heuristic methods}
Explanation of what heuristic methods is.\\
Heuristic search methods is an approximate method, for situation when a optimal solutions is not required, or is to expensive to calculate. \\Even if it does not find the best solution, it "is guaranteed to find a good solution in reasonable time." (http://www.cs.cf.ac.uk/Dave/AI2/node23.html).

\section{Problem formulation}
Our problem formulation was "To test implementation of greedy approach, tabu search and genetic programming and evaluation."


\subsection{Approach}
A description of our approach of the problem. We started by creating a simulation environment and decided which heuristic algorithms we were to use. Thereafter we thought of how to use the algorithms to solve the problem.

\subsection{The problem}
In addition to solve the problem by heuristic methods we wanted to compare our results with the MILP approach, which is guaranteed to give optimal result, but is slower.